A Roadmap for\\HEP Software and Computing R\&D\\for the 2020s

### 2018-11-06 CWP/papers/HSF-CWP-2017-01_roadmap/latex/cwp-main.tex
Federated identities: clarify that it is non-X509

Although federated identity provides a potential solution for our
challenges in Authentication, Authorisation should continue to be
tightly controlled by the HEP community. Enabling Virtual Organisation
(VO) membership for federated credentials and integrating such a
workflow with existing identity vetting processes is a major topic
currently being worked on, in particular within the WLCG community.
Commercial clouds and HPC centres have fundamentally different access
control models and technologies from our grid environment. We shall need
to enhance our access control model to ensure compatibility and
translate our grid-based identity attributes into those consumable by
such services.

>>>>

Although non-X509 federated identity provides a potential solution for our
challenges in Authentication, Authorisation should continue to be
tightly controlled by the HEP community. Enabling Virtual Organisation
(VO) membership for federated credentials and integrating such a
workflow with existing identity vetting processes is a major topic
currently being worked on, in particular within the WLCG community.
Commercial clouds and HPC centres have fundamentally different access
control models and technologies from our grid environment. We shall need
to enhance our access control model to ensure compatibility and
translate our grid-based identity attributes into those consumable by
such services.
